\input{tables/assessment_scale}

\leadin{Wikipedia assessment ratings.} Wikipedians assign quality assessments to articles based on a scale that was originally developed to produce an official "1.0" version of Wikipedia\footnote{\url{https://en.wikipedia.org/wiki/Wikipedia:Version_1.0_Editorial_Team}}.  This scale has since been adopted by WikiProjects\footnote{\url{https://en.wikipedia.org/wiki/WikiProject}}, self-organized subject-matter focused working groups on Wikipedia (\emph{e.g.} WikiProject Video Games, WikiProject Medicine, and WikiProject Breakfast).  Table~\ref{tab:assessment_scale} shows the rating scale with defunct old grades ("A", "B+", etc.) removed.  Wikipedians use this scale to track progress towards content coverage goals and to build work lists (\emph{e.g.} WikiProject Medicine's tasks\footnote{\url{https://en.wikipedia.org/wiki/Wikipedia:WikiProject_Medicine/Tools\#Tasks}}).

Both Kittur et al.\cite{kittur08harnessing} and Arazy \& Nov\cite{arazy10determinants} used article quality assessments provided by Wikipedians to track article improvements and to find correlations with editor activity and experience level characteristics.  They use these correlations to draw conclusions about successful collaboration patterns.  Regretfully, the process by which Wikipedians assess and re-assess articles is unpredictable.  We can be relatively sure of the quality level of an article at the time it was assessed, but there's no clear way to know when, exactly, the quality level of an article actually changed.  The aforementioned studies use a set of complex propensity modeling strategies like Heckman Correction\footnote{\url{https://en.wikipedia.org/wiki/Heckman_correction}} to minimize the possibility that the correlations they observe were simply due to the \emph{assessment} behavior of Wikipedians and not actual changes in article quality.  The modeling of correction is difficult to optimize and evaluate independently of the effects that editor collaboration patterns may have had on those quality changes.  Further, past analyses have been limited to the times at which Wikipedians were performing assessments of articles.  Assessments didn't become common until 2006 (5 years after Wikipedia's inception) and the criteria by which articles are assessed has been undergoing changes since then.  Articles that were "B" class in 2006 would likely now be classified as a "Start" class due to insufficient inline references.  Table~\ref{tab:b_class_criteria} shows the change in B-class criteria between 2006 and 2017.

Further, the fact that assessments are sparse and unpredictable also means that the assessment are often out of date.  This is an operational issue for Wikipedians too.  WikiProject groups organize re-assessment drives to bring the assessments of articles under their purview into compliance, but this is a never-ending process.  Since Wikipedia contributions come from anyone (member of the WikiProject or not) and re-assessments are uncommon despite regular coordinated efforts, the overall assessments of Wikipedia articles are perpetually out of date and reassessments are a never-ending source of new work.

\input{tables/b_class_criteria}
